Model of lens candidates from Space Warps CFHTLS

### 2016-07-11 paper2.tex
edits

\subsection{HiRes / Subsampling of central region}
In a previous paper \cite{2015MNRAS.447.2170K} we identified the problem of the tendency of the models to be too shallow.
We pinned down the problem to the central region and are confident to have it fixed with enabling sub pixel sampling in the central area.
The software allows for subsampling parameters of radius of pixels $r_\text{subs}$ and amount of subpixels per pixel $n_\text{subs}$.
\figref{subsampling} shows the results of different settings for $r_\text{subs}$ and $n_\text{subs}$.
We can see that even the computationally least expensive settings of $r_\text{subs}=1$ and $n_\text{subs}=3$ leads to drastically improved profiles.

@@

In this section, we discuss ten systems.

>>>>

\subsection{HiRes / Subsampling of central region}
In a previous paper \cite{2015MNRAS.447.2170K} we identified the problem of the tendency of the models to be too shallow.
We pinned down the problem to the central region and are confident to have it fixed with enabling sub pixel sampling in the central area.
The software allows for subsampling parameters of radius of pixels $r_\text{subs}$ and amount of subpixels per pixel $n_\text{subs}$.
Figure~\figref{subsampling} shows the results of different settings for $r_\text{subs}$ and $n_\text{subs}$.
We can see that even the computationally least expensive settings of $r_\text{subs}=1$ and $n_\text{subs}=3$ leads to drastically improved profiles.

@@

In this section, we discuss ten systems, including the five systems
most convincingly modelled, but also cases where modelling failed.
